\chapter{Abstract}

\paragraph{}
The Startup INSBI (Institute Business Intelligence) is a newly created company which in its offer has a list of service that revolves around solutions of digitalization of companies and business intelligence. In order to make a name for itself in the market INSBI has produced and launched its first product which is Hosteline. Hosteline is an online hospitality platform that targets hotel owners and places their premises at the disposal of customers who in turn can book these different premises. Hosteline is a web portal that brings together hotels and provides comparative access to customers of this platform. Through this platform, hotel customers will have advantages both in terms of prices and the facilities that these hotels can offer thanks to its loyalty program. This system when put into production will generate a large amount of data through its transactional system. Knowing how useful these data are but not enough in the raw state, the INSBI management wants to set up a decision-making system to be able to exploit this data and to draw the strategic choices and decisions to make the product grow offering a better quality of service to its consumers. These is where we came into the game to set up a Reporting system that will serve data from operational systems in readable and easily interpretable formats. Our job was to give satisfaction to a specific need recorded in a specifications book with well-defined cost and time constraints. In this thesis we will highlight, the working method, the evolution of the work at INSBI and the follow-up that was ours throughout the duration of our internship. Thanks to this project we could put into practice lessons learned during our training and it permitted us to learn more about business intelligence and many other new concepts.